Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

>>>>

\documentclass[conference]{configs/IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
%\usepackage[table,xcdraw]{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{table}[!htb]
	\label{testcases}
	\caption{Test Cases}
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}
